---
title: "House Price 6 days"
author: "Zahra N."
date: "2/24/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r cars}
path <- "~/Documents/R Programming/HousePrice"
setwd (path)
getwd()
```

#Reading Data

``` {r}
traindata <- read.csv("train.csv")
backuptraindata <-traindata
head(traindata, 5)
summary(traindata)
str(traindata)
tail(traindata, 5)
dim(traindata)
read.csv("train.csv")

```


# package
``` {r}
install.packages("nnet")
library(nnet)

```
#Regression
``` {r}
multinom(as.factor(SalePrice[1:10]) ~ SaleType[1:10] + GarageCond[1:10], data=(traindata))

traindata$SalePrice[1:10]

```
#Regression
??lim
``` {r}

lm(SalePrice~SaleType + GarageCond, traindata)


lm(loss~.,AllState.Dataframe)

model <-glm(formula = Survived~ Fare + Age, data = Datatrain, family = "binomial")

#--------Hajar
glm(formula = SalePrice ~ as.factor(SaleType) + MSSubClass, data=traindata)
traindata$SalePrice

```
## Missing Data

traindata[!complete.cases(traindata$MSSubClass), 2 ]
traindata[!complete.cases(traindata$MSZoning), 2 ]
traindata[!complete.cases(traindata$LotFrontage), 2 ]
traindata[!complete.cases(traindata$LotFrontage), 4 ] <-0
traindata[!complete.cases(traindata$LotArea), 1] # Ok, no missing
traindata[!complete.cases(traindata$Street), 1] # ok, no missing
traindata[!complete.cases(traindata$Alley), c(1,7)] 
## Alot of missing!!! you may delete the Alley variable
traindata[!complete.cases(traindata$LotShape), c(1,8)]  ## no missing
traindata[!complete.cases(traindata$LandContour), 9]   ## no missing
traindata[!complete.cases(traindata$Utilities), 10]   ##no missing
traindata[!complete.cases(traindata$LotConfig), 11]   ##no missing
traindata[!complete.cases(traindata$LandSlope), 12]   ##no missing
traindata[!complete.cases(traindata$Neighborhood), 13]   ##no missing

traindata[!complete.cases(traindata$Condition1), 14]   ##no missing
traindata[!complete.cases(traindata$Condition2), 15]   ##no missing

traindata[!complete.cases(traindata$BldgType), 16]   ##no missing
traindata[!complete.cases(traindata$HouseStyle), 17]   ##no missing
traindata[!complete.cases(traindata$OverallQual), 18]   ##no missing
## Overall Quality can turn into ordinal/factor
traindata[!complete.cases(traindata$ OverallCond), 19]   ##no missing


traindata[!complete.cases(traindata$YearBuilt), 20]   ##no missing
traindata$YearBuilt <-as.(traindata$YearBuilt)???
traindata[!complete.cases(traindata$YearRemodAdd), 21]   ##no missing
traindata[!complete.cases(traindata$RoofStyle), 22]

traindata[!complete.cases(traindata$RoofMatl), 23]
traindata[!complete.cases(traindata$Exterior1st), 24]
traindata[!complete.cases(traindata$Exterior2nd), 25]
traindata[!complete.cases(traindata$MasVnrType), 26]
traindata[!complete.cases(traindata$MasVnrType), c(1,26)] ## Missing Data


traindata[!complete.cases(traindata$MasVnrArea), 27]
traindata[!complete.cases(traindata$MasVnrArea), c(1,27)] ## 0 looks like a mode

traindata[!complete.cases(traindata$ExterQual), c(1,28)]
traindata[!complete.cases(traindata$ExterCond), 29]

traindata[!complete.cases(traindata$Foundation),30]
traindata[!complete.cases(traindata$BsmtQual),31] # Missing
traindata[!complete.cases(traindata$BsmtCond), 32] # Missing


traindata[!complete.cases(traindata$BsmtExposure),33] #Missing
traindata[!complete.cases(traindata$ BsmtFinType1),34] #Missing
traindata[!complete.cases(traindata$BsmtFinSF1),35]

traindata[!complete.cases(traindata$BsmtFinType2),36] #Missing
traindata[!complete.cases(traindata$BsmtFinSF2),37]
traindata[!complete.cases(traindata$BsmtUnfSF),38]
traindata[!complete.cases(traindata$TotalBsmtSF),39]


str(traindata[ , 40:49])
traindata[!complete.cases(traindata$Heating),40]
traindata[!complete.cases(traindata$HeatingQC),41]
traindata[!complete.cases(traindata$CentralAir),42]
traindata[!complete.cases(traindata$Electrical),43] one missing
traindata[!complete.cases(traindata$X1stFlrSF),44]
traindata[!complete.cases(traindata$X2ndFlrSF),45]
traindata[!complete.cases(traindata$LowQualFinSF),46]
traindata[!complete.cases(traindata$GrLivArea),47]
traindata[!complete.cases(traindata$BsmtFullBath),48]
traindata[!complete.cases(traindata$BsmtHalfBath),49]

str(traindata[ , 50:59])
traindata[!complete.cases(traindata$FullBath),50]
traindata[!complete.cases(traindata$HalfBath),51]
traindata[!complete.cases(traindata$BedroomAbvGr),52]
traindata[!complete.cases(traindata$KitchenAbvGr),53]
traindata[!complete.cases(traindata$KitchenQual),54]
traindata[!complete.cases(traindata$TotRmsAbvGrd),55]
traindata[!complete.cases(traindata$Functional),56]
traindata[!complete.cases(traindata$Fireplaces),57] 
traindata[!complete.cases(traindata$FireplaceQu),58] # Many missing data
traindata[!complete.cases(traindata$GarageType),59]  # Many missing data

str(traindata[ , 60:69])
traindata[!complete.cases(traindata$GarageYrBlt),60] # Missing as NA
traindata[!complete.cases(traindata$GarageFinish),61] # Missing as <NA>
traindata[!complete.cases(traindata$GarageCars),62]
traindata[!complete.cases(traindata$GarageArea),63]
traindata[!complete.cases(traindata$GarageQual),64] # Missing
traindata[!complete.cases(traindata$GarageCond),65] # Missing
traindata[!complete.cases(traindata$PavedDrive),66]
traindata[!complete.cases(traindata$WoodDeckSF),67] 
traindata[!complete.cases(traindata$OpenPorchSF),68] 
traindata[!complete.cases(traindata$EnclosedPorch),69]  


str(traindata[ , 70:79])
traindata[!complete.cases(traindata$X3SsnPorch),70] 
traindata[!complete.cases(traindata$ScreenPorch),71] 
traindata[!complete.cases(traindata$PoolArea),72]
traindata[!complete.cases(traindata$PoolQC),73] ## a loooot missing
traindata[!complete.cases(traindata$Fence),74]  ## a looooot missing
traindata[!complete.cases(traindata$MiscFeature),75] ## a loooot missing
traindata[!complete.cases(traindata$MiscVal),76]
traindata[!complete.cases(traindata$MoSold),77] 
traindata[!complete.cases(traindata$YrSold),78] 
traindata[!complete.cases(traindata$SaleType),79] 

str(traindata)
str(traindata[ , 80:81])
traindata[!complete.cases(traindata$SaleCondition),80] 
traindata[!complete.cases(traindata$SalePrice),81] 













str(traindata)
str(traindata[, 1:5])
str(traindata[, 6:11])
str(traindata[ , 12:19])
str(traindata[ , 20:29])
str(traindata[ , 30:39])





for (i in seq_along(traindata)) {
traindata[!complete.cases(traindata),c(1:4)] 
}



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
